Analyzing the Effect of Surface in Tennis Grand Slams

### 2018-09-14 contest/surface-type/paper-tennis.Rmd
Put data in R package format and put pbp data in form of gs

```{r data-cleaning, include = FALSE}
## Load WTA and ATP matches from deuce package
data(atp_matches)
data(wta_matches)

## Clean data
gs <- clean_matches_data(atp_matches = atp_matches,
                         wta_matches = wta_matches,
                         start_year = 2013,
                         end_year = 2017,
                         include_quals = FALSE,
                         level = "Grand Slams")

## Extract sets, points, and games
gs <- extract_sgp(gs)

# devtools::use_data(gs, overwrite = TRUE)

## Make into player data
gs_players <- matches_to_player_data(gs,
                                     w_opp_vars = "loser_rank",
                                     l_opp_vars = "winner_rank",
                                     opp_var_names = "opponent_rank")

# devtools::use_data(gs_players, overwrite = TRUE)

>>>>

```{r data-cleaning, include = FALSE}
data(gs)
data(gs_players)
data(gs_partial)
data(gs_partial_players)
